openarchaeoCollaboration

### 2021-02-27 analysis/paper.Rmd
Update GitHub API data
And backup intermediate data in analysis/derived_data/

```{r data-oarch}
oarch <- read_csv("https://raw.githubusercontent.com/zackbatist/open-archaeo/master/open-archaeo.csv")
```

@@

```{r data-github}
# Pretty slow
oarch %>% 
  mutate(
    gh_repo = str_remove(github, "https://github.com/"),
    gh_repo = str_remove(gh_repo, "/$")
  ) %>% 
  separate(gh_repo, c("gh_owner", "gh_repo"), "/", 
           fill = "right", extra = "drop") %>% 
  mutate(
    gh_lang = ght("GET /repos/{owner}/{repo}/languages", 
                  owner = gh_owner, repo = gh_repo),
    gh_contributors = ght("GET /repos/{owner}/{repo}/contributors",
                          owner = gh_owner, repo = gh_repo)
  ) ->
  oarch
```

@@

### What languages are people using?

@@

### Who is contributing?

```{r plot-gh_contributors-by-repo}
oarch %>% 
  unnest(gh_contributors) %>% 
  mutate(gh_repo = paste(gh_owner, gh_repo, sep = "/")) %>% 
  group_by(gh_repo) %>% 
  summarise(n = n(), .groups = "drop") %>% 
  ggplot(aes(fct_reorder(gh_repo, n, .desc = TRUE), n)) +
  geom_col() +
  labs(
    title = "Repositories by number of contributors",
    caption = "Data: <https://open-archaeo.info> and the GitHub API",
    x = "Repository", y = "Number of contributors"
  ) +
  theme(axis.text.x = element_blank())
```

>>>>

```{r data-oarch}
read_csv("https://raw.githubusercontent.com/zackbatist/open-archaeo/master/open-archaeo.csv") %>% 
  mutate(category = na_if(category, "?")) %>% 
  mutate(gh_repo = str_remove(github, "https://github.com/")) ->
  oarch
```

@@

```{r data-github}
# Warning: slow
# TODO: map
gh_langs <- map(oarch$gh_repo, gh_lang)
gh_contribs <- map(oarch$gh_repo, gh_contrib)
gh_issues <- map(oarch$gh_repo, gh_issue)
gh_comments <- map(oarch$gh_repo, gh_comment)
gh_commits <- map(oarch$gh_repo, function(x) { print(x); gh_commit(x) })
```

@@

### Tags and categories

```{r plot-categories}
oarch %>% 
  group_by(category) %>% 
  drop_na(category) %>% 
  summarise(n = n()) %>% 
  ggplot(aes(fct_reorder(category, n), n)) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Open archaeology categories",
    caption = "Data: <https://open-archaeo.info>",
    x = NULL, y = "Number of projects"
  )
```

```{r plot-tags}
oarch %>% 
  pivot_longer(c(tag1, tag2, tag3, tag4, tag5), values_to = "tag", 
               values_drop_na = TRUE) %>% 
  group_by(tag) %>%
  drop_na(tag) %>%
  summarise(n = n()) %>%
  ggplot(aes(fct_reorder(tag, n), n)) +
  geom_col() +
  coord_flip() +
  labs(
    title = "Open archaeology tags",
    caption = "Data: <https://open-archaeo.info>",
    x = NULL, y = "Number of projects"
  )
```

### Use of GitHub

@@

### Repository contributors

```{r plot-gh_contributors-histogram}
oarch %>% 
  drop_na(gh_repo) %>% 
  unnest(gh_contributors) %>% 
  mutate(gh_repo = paste(gh_owner, gh_repo, sep = "/")) %>% 
  group_by(gh_repo) %>% 
  summarise(n = n(), .groups = "drop") %>% 
  ggplot(aes(x = n)) +
  geom_histogram(binwidth = 1) +
  labs(
    title = "Repositories by number of contributors",
    caption = "Data: <https://open-archaeo.info> and the GitHub API",
    x = "Contributors", y = "Repositories"
  )
```
